---
title: "DeshmukhPranjaliHW-2"
author: "Pranjali Deshmukh"
date: "`r Sys.Date()`"
output: pdf_document
---

## R Markdown
Q1. a) A bar graph showing the number of zipcodes in each NYC borough:
```{r Bargraph}
State_count<-read.csv( "CovidData-NYStateDailyCounts.csv",header=T)
Zip_count<-read.csv("CovidData-NYCZipcodeCounts.csv" ,header=T)
library(ggplot2)
ggplot(Zip_count,mapping=aes(x=BOROUGH_GROUP))+geom_bar()
```


b)Histogram of the number of Covid cases by zipcode, using a bin width of 100:
```{r HISTOGRAM}
 ggplot(Zip_count)+geom_histogram(mapping=aes(x=COVID_CASE_COUNT), binwidth=100)
```
c) Similar to a histogram of the number of Covid cases by zipcode, using a bin width of
100, but with the bars represented by points instead:
```{r}
ggplot(Zip_count, aes(x=COVID_CASE_COUNT))+stat_bin(geom="point",binwidth=100)
```

(d) Side-by-side boxplots of the total number of tests conducted in each zipcode:
```{r}
ggplot(Zip_count, aes(x=BOROUGH_GROUP, y=TOTAL_COVID_TESTS))+geom_boxplot()
```
(e) Scatter plot of Covid deaths by zipcode vs Percent positive by zipcode:
```{r}
ggplot(Zip_count,aes(x=PERCENT_POSITIVE,y=COVID_DEATH_COUNT))+geom_point(aes(color=BOROUGH_GROUP,shape=BOROUGH_GROUP))
```
(f) Scatter plot of zipcode deaths vs case counts, separated by borough and with a fitted
line:
```{r}
p<-ggplot(Zip_count,aes(x=PERCENT_POSITIVE,y=COVID_DEATH_COUNT))+geom_point()
p+facet_grid(rows=vars(BOROUGH_GROUP))+stat_smooth(method="lm",color='red',se=FALSE)
```
(g) A timeplot of the daily number of cases and number of deaths:
```{r}
qplot(xlab="Day1 is Feb 29,2020",ylab="Number of cases and deaths")+geom_point(data=State_count, aes(x=1:127,y=Cases),)+geom_line(data=State_count,aes(x=1:127,y=Deaths))
```
(h) Scatter plot of the daily number of deaths vs daily number of cases:
```{r}
ggplot(State_count,aes(x=Cases,y=Deaths,color=Hospitalizations))+geom_point(shape=3)
```
(i) Scatter plot of the daily proportion of deaths to cases, vs number of cases:
```{r}
qplot(data=State_count,xlab="Cases", ylab="Proportion of deaths to cases",x=Cases, y=Deaths/Cases,  color=Hospitalizations,geom="point")
```
Q2(a)
```{r, echo=FALSE}
sprintf("The total number of cases in NYC is %d ", sum(Zip_count$TOTAL_COVID_TESTS))
```
Q2 (b) Summary of numerical columns of Covidbyzip.
```{r,echo=FALSE}
sapply(Zip_count[,c(1,4:10)], summary)
```
Q2(c) Summary statics for Manhattan zipcode only.
```{r,echo=FALSE}

sapply(Zip_count[Zip_count$BOROUGH_GROUP== "Manhattan", c(1,4:10)], summary) 
```
Q2(d)Summary statics for Queens zipcode only.
```{r,echo=FALSE}
sapply(Zip_count[Zip_count$BOROUGH_GROUP== "Queens", c(1,4:10)], summary)
```
Q2(d)Summary statics for Staten Island zipcode only.
```{r,echo=FALSE}

sapply(Zip_count[Zip_count$BOROUGH_GROUP== "Staten Island", c(1,4:10)], summary)
```
Q2e)
```{r, echo=FALSE}
b<-max(Zip_count$COVID_CASE_RATE)
a<-Zip_count[Zip_count$COVID_CASE_RATE==b,]
sprintf("The NYC zipcode & neighborhood name with the highest case rate %d, %s",a$MODIFIED_ZCTA,a$NEIGHBORHOOD_NAME)
```
Q2(F)Down below are the days in which most number of deaths happened relative to hospitalizations in NY State.
```{r,echo=FALSE}
State_count[State_count$Deaths>State_count$Hospitalizations,]
```
Q3.(a) Use seq to create a vector with elements 2, 4, 6, ... to 24. Extract the 5th value of this
vector.
```{r,echo=FALSE}
a<-seq(2,24,by=2)
a[5]
```
(b) Reverse the order of your vector above.
```{r}
rev(a)
```
(c) Create a vector consisting of, fifty 1’s, twenty-six 2’s and seventeen 3’s, in that order.
```{r}
b<-rep(c(1,2,3),times=c(50,26,17))
b
```
(d) Create a diagonal matrix with the numbers 1, 2, 3, ... 10 in the diagonal. Find its
inverse.
```{r}
mat<-diag(c(1:10))
mat
x<-solve(mat)
x
```
(e) Extract the 5th column of the matrix you created in 3(d). Make this vector (i.e the 5th
column) into a 2 ×5 matrix, fillng out the matrix by row.
```{r}
matrix(x[,3], c(2,5), byrow = TRUE )
```

