---
title: "DeshmukhPranjali-HW3"
author: "Pranjali Deshmukh"
date: "`r Sys.Date()`"
output:
  pdf_document: default

---

```{r}
library(tidyverse)
team_stats=read_csv("teamstats-1920.csv",show_col_types = FALSE)
teamgoalkeeping=read_csv("teamgoalkeeping-1920.csv",show_col_types = FALSE)
players=read_csv("players-1920.csv",show_col_types = FALSE)
standings=read_csv("standings-1920.csv",show_col_types = FALSE)
goalkeeper=read_csv("goalkeepers-1920.csv",show_col_types = FALSE)
scoresfixtures=read_csv("scoresfixtures-1920.csv",show_col_types = FALSE)
```
##Q1a)Nuumber of teams in league
```{r}
NROW(team_stats)
```
##Q1b)Number of players in team
```{r}
NROW(unique(players))
```
##Q1c)Total numbers of goals scored
```{r}
sum(players$Gls)
```
##Q1d)Average attendance at games is
```{r}
mean(standings$Attendance)
```
##Q2) "squad" is the primary key for tables team statics,team goalkeeping and standings."Player" is the primary key for goalkeepers table. 
```{r}
standings%>%count(Squad)%>%filter(n>1)
team_stats%>%count(Squad)%>%filter(n>1)
teamgoalkeeping%>%count(Squad)%>%filter(n>1)
goalkeeper%>%count(Player)%>%filter(n>1)
```
##Q3 Squad connects standings, team statics and team goalkeeping to each other so its the foreign key for one and primary for latter.


##Q4 Players and goalkeepers table with first version of 
```{r, "Question 4"}
df<-players%>%separate(Player, into = c("Player","2nd ed"), sep = "\\\\")
df<-df%>%separate(Nation, into = c("N1","N2"))
New_players<-df[,c(1,2,4:31)]
print(New_players, n=10)
df1<-goalkeeper%>%separate(Player, into = c("Player","2nd ed"), sep = "\\\\")
df1<-df1%>%separate(Nation, into = c("N1","N2"))
New_goalkeeper<-df1[,c(1,2,4:26)]
print(New_goalkeeper,n=10)
```
##Q5.Information of players 
```{r, Question 5}
age<-players%>%group_by(Squad)%>%summarize(mean=mean(Age, na.rm=TRUE),min=min(Age,na.rm =TRUE),max=max(Age,na.rm=TRUE),Youngest_player=Player[which.min(Age)])
print(age,n=10)
```
Q6
```{r}
df2<-team_stats[,c(1,3,8)]
df3<-teamgoalkeeping[,c(1,10,15,14,17)]
standings<-standings%>%left_join(df2)
standings<-standings%>%left_join(df3)
standings<-standings%>%left_join(age)
```
##Q6a)Points attained vs Possession
```{r}
ggplot(data=standings,aes(x=Poss,y=Pts))+geom_line()
```
##Q6 b)Points attained vs Save percentage
```{r}
ggplot(data=standings,aes(x='Save%',y=Pts))+geom_point()
```
##Q6c)Points attained vs Goal against
```{r}
ggplot(data=standings,aes(x=GA,y=Pts))+geom_point()
```
##Q6d)Clean sheet percentage vs Save percentage
```{r}
ggplot(data=standings,aes(x='Save%',y=CS))+geom_point()
```
##Q7 Top 3 referees
````{r}
referees<-scoresfixtures %>% count(Referee,sort = TRUE) %>% slice(1:3)
referees
top_3_referee<-c(referees[,1])
top_3_referee
scoresfixtures %>% group_by(Referee) %>% select(Wk,Date,Home,Away) %>% filter(Referee=="Anthony Taylor" | Referee=="Martin Atkinson" | Referee=="Michael Oliver" )
```
##Q8 Top 3 teams
```{r}
scores1<-team_stats%>%arrange(desc(Gls))
top_3_scoring<-scores1[c(1,2,3),c(1)]
top_3_scoring
scoresfixtures %>% select(Wk,Date,Home,Away,Score) %>% filter((Home=="Manchester City"| Home =="Liverpool" | Home=="Chelsea") & (Away=="Manchester City"| Away =="Liverpool" | Away=="Chelsea"))
```
##Q9 Top 3 dates with most games played
```{r}
Dates<-scoresfixtures%>%group_by(Date)%>%count(Date,sort=TRUE)
top_3_days<-Dates[c(1,2,3),c(1)]
top_3_days
list_of_games<-scoresfixtures%>%select(everything())%>%filter(Date==as.Date("2020-07-26") | Date==as.Date("2019-12-26") | Date==as.Date("2020-01-01"))
list_of_games
```
##Q10 Dates with most scored goals 
```{r}
xyz<-scoresfixtures%>%select(Date,Score,Home)%>%filter(Home=="Manchester City"| Home =="Liverpool" | Home=="Chelsea")%>%arrange(desc(Score))
xyz<-xyz[c(1,2,3),c(1)]
xyz
```