---
title: "DeshmukhPranjali-HW4"
author: "Pranjali Deshmukh"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

##Q1 Write a function to evaluate ab given a and b.
```{r}
myfun<-function(a,b){a^b}
myfun(2,3)
```
##Q2 Write a function that accepts two arguments, a number and a vector, and returns TRUE if the number is inside the vector.

```{r cars}
myfun1<-function(x,y){ 
  for(a in y){
    if(a==x){
      return(TRUE)
    }
  }
  return(FALSE)
}
myfun1(x=3, y=c(1,2,3))
```
##Q3Write a function that, given a number and a vector, will return the number of times the number occurs in the vector.
```{r}
myfun2<-function(x,y){
  count=0
  for(a in y){
    if(a==x){
    count=count+1 }
  }
  return(count)
}
myfun2(x=1,y=c(1,2,1,1,1,2))
```
##Q4Use the mtcars dataset for this question. Use one of the apply functions to find the mean of every column in mtcars.
```{r}
sapply(mtcars, mean)
```
##Q5 Fibonacci series 
```{r}
myf<-function(x){
 first=0
 second=1
 temp=0
 if(x==0){
   return(first)
 }
 else if(x==1){
   return(second)
 }
 else{
 for(n in 2:x){
  temp=first+second
  first=second
  second=temp
  n=n+1
 }
 return(temp)}

}
myf(20)
myf(80)
```
##Q6 Taylor's expression
```{r}
a=function(x,n)
{
  a=0
  temp=0
  ans=1
  while(a<=n){
    temp=temp+myfun(x,a)/ans
    a=a+1
    ans=ans*a
  }
 return(c(temp,exp(x)-temp))
}
a(3,10)
a(0.44,3)
```
##Q7 Factorial
```{r}
b=function(n){
  ans=1
  for (i in 1:n){
    ans=ans*i
  }
  return(ans)
}
b(3)
Fact<- function(N)
{
if (N == 0){
return(1)}
else {return( N * Fact(N-1))}
}
Fact(3)
```
##Q8Write a function that accepts a vector of numbers (of length >= 4) and returns a vector of moving averages, i.e. with x = (x1, . . . , xn), the output is a vector with the values
```{r}
movavg<-function(y){
  d=0
  vect=c()
  if(length(y)>=4){
    for (i in 1:length(y)-3){
      d=(y[i]+y[i+1]+y[i+2]+y[i+3])/4
      vect<-c(vect, d)
    }
  vect
  }
}
y <- c(1, 1, 2, 5, 8, 3, 4, -4, 3, 7, 2, 2, -2, 1)
movavg(y)
```
##Q9 Write an R function that accepts a vector of numbers and returns the values of the function evaluated using that vector of numbers.
```{r}
myfun3<-function(y){
  d=0
  vect=c()
  for (x in y){
    if(x<0){
      d=x^2+2*x+3
      vect<-c(vect,d)
    }
    else if(x>=0 & x<2 ){
      d=x+3
      vect<-c(vect,d)
    }
    else{
      d=x^2+4*x-7
      vect<-c(vect,d)
    }
  }
  plot(vect)
  vect
  }
myfun3(c(-2,-1,0,1,2,3))
```

##Q10

```{r}
set.seed(20330)
mydata <- rgamma(100, shape=4, scale=5)
make.NegLogLik <- function(data, fixed=c(FALSE, FALSE)){
  params <- fixed
  function(param.values){
    params[!fixed] <- param.values
    a <- params[1]
    b <- params[2]
    value <- (a-1)* sum(log(data)) -length(data) * log(gamma(a)) -(length(data) * a) * log(b) - (1/b) * sum(data)
    value
  }
}
my.negloglik <- make.NegLogLik(mydata)
```

```{r warning = FALSE}
optim(c(a=2,b=2), my.negloglik)$par
```

